Dispersion of short waves riding on longer waves

### 2024-05-14 paper/paper.tex
Fix sign in 3rd order grav. accel.

Equations (\ref{eq:dispersion}) and (\ref{eq:wave_crests}) only describe the
evolution of the wavenumber.
To describe the evolution of the wave amplitude, we use the conservation of wave
action in absence of sources (e.g. due to wind) and sinks (e.g. due to whitecapping):

@@

For the ambient forcing, we consider a single, monochromatic long wave
defined by the elevation $\eta_L = a_L cos{\psi}$,
where $a_L$ is the long-wave amplitude, $\psi = k_L x - \omega_L t$ is the
long-wave phase, and $\omega_L$ its angular frequency.
At this time we define the long-wave steepness $\varepsilon_L = a_L k_L$ which
we will use thoughout the rest of the paper as a scaling parameter.
The long wave induces horizontal and vertical orbital velocities whose values
at the surface $\eta_L$ are:

>>>>

Equations (\ref{eq:dispersion}) and (\ref{eq:wave_crests}) only describe the
evolution of the short-wave wavenumber.
To describe the evolution of the wave amplitude, we use the conservation of wave
action in absence of sources (e.g. due to wind) and sinks (e.g. due to whitecapping):

@@

For the ambient forcing, we consider a train of monochromatic long wave
defined, to the first order in steepness, by the elevation $\eta_L = a_L cos{\psi}$,
where $a_L$ is the long-wave amplitude, $\psi = k_L x - \omega_L t$ is the
long-wave phase, and $\omega_L$ its angular frequency.

At this time we define the long-wave steepness $\varepsilon_L = a_L k_L$ which
we will use thoughout the rest of the paper as a scaling parameter.
The long wave induces horizontal and vertical orbital velocities whose values
at the surface $\eta_L$ are:
